---
title: "Revise and Resubmit Analyses"
author: "Joel Larwood"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---
#####


NEW STUFF

```{r}
devtools::install_github("centerforopenscience/osfr", force = FALSE)
library(tidyverse)
osfr::osf_retrieve_file("nc9jp") %>% osfr::osf_download(overwrite = T)
dat <- read_csv("Data with Depression.csv")
```


```{r}
#count p's
nrow(dat)
#visualise missing data 
xfun::pkg_attach2("naniar")
dat %>% select(contains("MUVA"),
                   contains("MUAR"),
                   contains("TAS"),
                   contains("DASS")) %>% vis_miss()
#no missing data 
```


```{r}
#create working data frame

cleanrr <- dat 
```

```{r safe alexithymia original}
cleanrr$rTAS4_1 <- cleanrr$TAS4_1
cleanrr$rTAS5_1 <- cleanrr$TAS5_1
cleanrr$rTAS10_1 <- cleanrr$TAS10_1
cleanrr$rTAS18_1 <- cleanrr$TAS18_1
cleanrr$rTAS19_1 <- cleanrr$TAS19_1
```

```{r alexithymia recode}
cleanrr$TAS4_1 <- 6 - cleanrr$rTAS4_1
cleanrr$TAS5_1 <- 6 - cleanrr$rTAS5_1
cleanrr$TAS10_1 <- 6 - cleanrr$rTAS10_1
cleanrr$TAS18_1 <- 6 - cleanrr$rTAS18_1
cleanrr$TAS19_1 <- 6 - cleanrr$rTAS19_1
```

```{r create alexithymia}
cleanrr$alexithymia <- cleanrr %>% select (contains("TAS"),
                                   -contains("rTAS")) %>% rowSums()

library("psych")
library("sjmisc")
TASalpha <- cleanrr %>% select (contains("TAS"),
                -contains("rTAS")) %>% psych::alpha()

cleanrr$dif <- cleanrr %>% select(TAS1_1, TAS3_1, TAS6_1, TAS7_1, TAS9_1, TAS13_1, TAS14_1) %>% rowSums()

DIFalpha <- cleanrr %>% select(TAS1_1, TAS3_1, TAS6_1, TAS7_1, TAS9_1, TAS13_1, TAS14_1) %>% alpha()

cleanrr$ddf <- cleanrr %>% select(TAS2_1, TAS4_1, TAS11_1, TAS12_1, TAS17_1) %>% rowSums()

DDFalpha <- cleanrr %>% select(TAS2_1, TAS4_1, TAS11_1, TAS12_1, TAS17_1) %>% alpha()

cleanrr$eot <- cleanrr %>% select(TAS5_1, TAS8_1, TAS10_1, TAS15_1, TAS18_1, TAS19_1, TAS20_1) %>% rowSums()

EOTalpha <- cleanrr %>% select(TAS5_1, TAS8_1, TAS10_1, TAS15_1, TAS18_1, TAS19_1, TAS20_1) %>% alpha()

cleanrr$clinicalalex <- dicho(cleanrr$alexithymia, dich.by = 50)
```

```{r create dass}
D <- c("DASS3_1", "DASS10_1", "DASS13_1", "DASS16_1", "DASS17_1", "DASS21_1")
DASSaplha <- cleanrr %>% select(D) %>% alpha()
cleanrr$depression <- cleanrr %>% select(D) %>% rowSums()
```

```{r lexicon}
cleanrr$pos.lex.count <- ((cleanrr$posemo*cleanrr$WC)/100)
#round 
cleanrr$pos.lex.count <- round(cleanrr$pos.lex.count, digits = 0)
cleanrr$neg.lex.count <- ((cleanrr$negemo*cleanrr$WC)/100)
cleanrr$neg.lex.count <- round(cleanrr$neg.lex.count, digits = 0)
cleanrr$emo.lex.count <- cleanrr$neg.lex.count + cleanrr$pos.lex.count
xfun::pkg_attach2("psych")
psych::describe(select(cleanrr, contains("count")))
```

```{r music score creation}
##--------Music Ratings
#Sad Music 
#Valence
cleanrr$sad.valence <- (cleanrr$MUVA31_1 + cleanrr$MUVA109_1) / 2
#AROUSAL 
cleanrr$sad.arousal <- (cleanrr$MUAR31_1 + cleanrr$MUAR109_1) / 2
#Angry music 
#Valence 
cleanrr$angry.valence <- (cleanrr$MUVA1_1 + cleanrr$MUVA69_1) / 2
#AROUSAL
cleanrr$angry.arousal <- (cleanrr$MUAR1_1 + cleanrr$MUAR69_1) / 2
#Fear Music
#VALENCE
cleanrr$fear.valence <- (cleanrr$MUVA11_1 + cleanrr$MUVA14_1) / 2
#AROUSAL
cleanrr$fear.arousal <- (cleanrr$MUAR11_1 + cleanrr$MUAR14_1) / 2
#Happy Music 
#VALENCE
cleanrr$happy.valence <- (cleanrr$MUVA23_1 + cleanrr$MUVA105_1) / 2 
#AROUSAL
cleanrr$happy.arousal = (cleanrr$MUAR23_1 + cleanrr$MUAR105_1) / 2
#Tender music 
#VALENCE
cleanrr$tender.valence <- (cleanrr$MUVA41_1 + cleanrr$MUVA42_1) / 2 
#AROUSAL
cleanrr$tender.arousal <- (cleanrr$MUAR41_1 + cleanrr$MUAR42_1) / 2 
```

```{r LexCor}
library(apaTables)
cleanrr %>% select(alexithymia, ddf, dif, eot, emo.lex.count, pos.lex.count, neg.lex.count) %>% apa.cor.table()
```

```{r reshape}
library(sjmisc)
long <- to_long(data = cleanrr,
  keys = "Emotion",
  values = c("Valence", "Arousal"),
  c ("sad.valence", "happy.valence", "fear.valence", "tender.valence", "angry.valence"),
  c ("sad.arousal", "happy.arousal", "fear.arousal", "tender.arousal", "angry.arousal")) %>%
  select(., id,
         Emotion,
         Valence,
         Arousal,
         alexithymia,
         ddf,
         dif,
         eot,
         depression) 

long$Emotion <- mapvalues (long$Emotion, from = c ("sad.valence", "happy.valence", "fear.valence", "tender.valence", "angry.valence"), to = c("Sad", "Happy", "Fearful", "Tender", "Angry"))
  
long$Emotion <- as.factor(long$Emotion)
long$Emotion <- relevel(long$Emotion, "Tender")
```

```{r describevalence}
long %>% group_by(Emotion) %>% dplyr::summarise(
  Mean = mean(Valence),
  SD = sd(Valence),
  Min = min(Valence),
  Max = max(Valence)) 
```

```{r describearousal}
long %>% group_by(Emotion) %>% dplyr::summarise(
  Mean = mean(Arousal),
  SD = sd(Arousal),
  Min = min(Arousal),
  Max = max(Arousal))  
```


```{r arousal glmm}
xfun::pkg_attach2("lme4")
arousalinteract <- glmer(arousal ~ 1 + alexithymia + condition + alexithymia*condition + (1|id), data = long)

xfun::pkg_attach2("lmerTest")
a.test <- as(arousalinteract,"merModLmerTest")
anova(a.test)

xfun::pkg_attach2("interactions")
interactions::sim_slopes(model = arousalinteract, pred = alexithymia , modx = condition, confint = TRUE)
```
## Plot model
```{r plot arousal}
xfun::pkg_attach2("jtools")
arousalplot <- interactions::interact_plot(model = arousalinteract, pred = alexithymia, modx = condition, interval = TRUE) + 
  theme_apa() + 
  geom_hline(yintercept = 0, linetype = "dotted") + labs (x = "Alexithymia", y = "Rated Arousal") 
arousalplot
```

##Depression in model
```{r arousal with depression}
arousalinteractdep <- glmer(arousal ~ 1 + depression + alexithymia + condition + alexithymia*condition + (1|id), data = long)
anova(arousalinteract, arousalinteractdep) %>% as.data.frame() %>% sjPlot::tab_df()
```

```{r valence glmm}
valenceinteract <- glmer(valence ~ 1 + alexithymia + condition + alexithymia*condition + (1|id), data = long)

sjPlot::tab_model(valenceinteract, arousalinteract)

xfun::pkg_attach2("lmerTest")
v.test <- as(valenceinteract,"merModLmerTest")
anova(v.test) 


xfun::pkg_attach2("interactions")
interactions::sim_slopes(model = valenceinteract, pred = alexithymia , modx = condition, confint = TRUE)
```
##Plot Model
```{r valence plot}
valenceplot <- interactions::interact_plot(model = valenceinteract, pred = alexithymia, modx = condition, interval = TRUE) + 
  theme_apa() + 
  geom_hline(yintercept = 0, linetype = "dotted") + labs (x = "Alexithymia", y = "Rated valence") 
valenceplot
```

##Depression in model 
```{r valence with depression}
valenceinteractdep <- lmer(valence ~ 1 + depression + alexithymia + condition + alexithymia*condition + (1|id), data = long)
xfun::pkg_attach2("htmlTable")
write_tableHTML(tableHTML(mtcars), file = 'myfile.html')

anova(valenceinteract, valenceinteractdep) %>% as.data.frame() %>% sjPlot::tab_df()
```






#Revise and Resubmit Analysis 

Additional Analyses as requested 

This script can be reproduced with data hosted on GitHub https://github.com/joellarwood/Alexithymia-and-Music-Affect-Perception/blob/master/Data%20with%20Depression.csv

Note: Data was collected as part of a larger project which contained depression scores, these have been included upon reviewer comments highlighting need to control for mood. 

```{r import and clean}
xfun::pkg_attach2("tidyverse")
reduced <- read_csv("https://raw.githubusercontent.com/joellarwood/NegAffectAlexithymiaMusicPerception-Bookdown/master/Data%20with%20Depression.csv")
#ensure only complete data is present 
table(reduced$Finished)
#count p's
nrow(reduced)
#visualise missing data 
xfun::pkg_attach2("naniar")
reduced %>% select(contains("MUVA"),
                   contains("MUAR"),
                   contains("TAS"),
                   contains("DASS")) %>% vis_miss()
#no missing data 
```
create woring data frame 'cleanrr' for analysis 
```{r}
cleanrr <- reduced
```

#make lexicon counts 

```{r lexicon}
cleanrr$pos.lex.count <- ((cleanrr$posemo*cleanrr$WC)/100)
#round 
cleanrr$pos.lex.count <- round(cleanrr$pos.lex.count, digits = 0)
cleanrr$neg.lex.count <- ((cleanrr$negemo*cleanrr$WC)/100)
cleanrr$neg.lex.count <- round(cleanrr$neg.lex.count, digits = 0)
cleanrr$emo.lex.count <- cleanrr$neg.lex.count + cleanrr$pos.lex.count
xfun::pkg_attach2("psych")
psych::describe(select(cleanrr, contains("count")))
```

#Get music scores 
```{r music score creation}
##--------Music Ratings
#Sad Music 
#Valence
cleanrr$sad.valence <- (cleanrr$MUVA31_1 + cleanrr$MUVA109_1) / 2
#AROUSAL 
cleanrr$sad.arousal <- (cleanrr$MUAR31_1 + cleanrr$MUAR109_1) / 2
#Angry music 
#Valence 
cleanrr$angry.valence <- (cleanrr$MUVA1_1 + cleanrr$MUVA69_1) / 2
#AROUSAL
cleanrr$angry.arousal <- (cleanrr$MUAR1_1 + cleanrr$MUAR69_1) / 2
#Fear Music
#VALENCE
cleanrr$fear.valence <- (cleanrr$MUVA11_1 + cleanrr$MUVA14_1) / 2
#AROUSAL
cleanrr$fear.arousal <- (cleanrr$MUAR11_1 + cleanrr$MUAR14_1) / 2
#Happy Music 
#VALENCE
cleanrr$happy.valence <- (cleanrr$MUVA23_1 + cleanrr$MUVA105_1) / 2 
#AROUSAL
cleanrr$happy.arousal = (cleanrr$MUAR23_1 + cleanrr$MUAR105_1) / 2
#Tender music 
#VALENCE
cleanrr$tender.valence <- (cleanrr$MUVA41_1 + cleanrr$MUVA42_1) / 2 
#AROUSAL
cleanrr$tender.arousal <- (cleanrr$MUAR41_1 + cleanrr$MUAR42_1) / 2 
```

#describe songs
```{r}
cleanrr %>% select(contains("valence"),
                   contains("arousal")) %>% psych::describe()
```

# Create alexithymia scores 

### Create safe variables for recoding to avoid double coding 

```{r}
cleanrr$rTAS4_1 <- cleanrr$TAS4_1
cleanrr$rTAS5_1 <- cleanrr$TAS5_1
cleanrr$rTAS10_1 <- cleanrr$TAS10_1
cleanrr$rTAS18_1 <- cleanrr$TAS18_1
cleanrr$rTAS19_1 <- cleanrr$TAS19_1
```

### Recode variables 
```{r}
cleanrr$TAS4_1 <- 6 - cleanrr$rTAS4_1
cleanrr$TAS5_1 <- 6 - cleanrr$rTAS5_1
cleanrr$TAS10_1 <- 6 - cleanrr$rTAS10_1
cleanrr$TAS18_1 <- 6 - cleanrr$rTAS18_1
cleanrr$TAS19_1 <- 6 - cleanrr$rTAS19_1
```

### Create TAS total and get descriptives
```{r}
xfun::pkg_attach2("tidyverse")
check <- cleanrr$alexithymia <- cleanrr %>% select (contains("TAS"),
                                   -contains("rTAS")) %>% rowSums()

xfun::pkg_attach2("psych")
cleanrr %>% select (contains("TAS"),
                -contains("rTAS")) %>% psych::alpha()

```

### Create difficulty identifying feelings 
```{r}
cleanrr$dif <- cleanrr %>% select(TAS1_1, TAS3_1, TAS6_1, TAS7_1, TAS9_1, TAS13_1, TAS14_1) %>% rowSums()

cleanrr %>% select(TAS1_1, TAS3_1, TAS6_1, TAS7_1, TAS9_1, TAS13_1, TAS14_1) %>% alpha()
```

### Create difficulty describing feeligns 
```{r}
cleanrr$ddf <- cleanrr %>% select(TAS2_1, TAS4_1, TAS11_1, TAS12_1, TAS17_1) %>% rowSums()

cleanrr %>% select(TAS2_1, TAS4_1, TAS11_1, TAS12_1, TAS17_1) %>% alpha()
```


### Create externally oriented thinking 
```{r}
cleanrr$eot <- cleanrr %>% select(TAS5_1, TAS8_1, TAS10_1, TAS15_1, TAS18_1, TAS19_1, TAS20_1) %>% rowSums()

cleanrr %>% select(TAS5_1, TAS8_1, TAS10_1, TAS15_1, TAS18_1, TAS19_1, TAS20_1) %>% alpha()

```
### Create cut-off
```{r above below cut-off}
xfun::pkg_attach2("sjmisc")
cleanrr$clinicalalex <- dicho(cleanrr$alexithymia, dich.by = 50)
cleanrr$clinicalalex<- factor(cleanrr$clinicalalex,
                                 levels = c(0,1),
                                 labels = c("below 51", "above 51"))
```
## Alexithymia descriptives
```{r describe alexithymia}
cleanrr %>% select(alexithymia, dif, ddf, eot) %>% describe()
table(cleanrr$clinicalalex)
```

#create DASS - depression subscale 
```{r create depression scores}
D <- c("DASS3_1", "DASS10_1", "DASS13_1", "DASS16_1", "DASS17_1", "DASS21_1")
cleanrr %>% select(D) %>% alpha()
cleanrr$depression <- cleanrr %>% select(D) %>% rowSums()
describe(cleanrr$depression)
```

# Correlation analyses lexicon data
```{r lexicon correlations}
cleanrr %>% select(alexithymia, ddf, dif, eot, emo.lex.count, pos.lex.count, neg.lex.count) %>% apaTables::apa.cor.table(filename = "lexcor.txt")
```

# Arousal GLMM
##Arousal data
```{r reshape arousal}
#give easy ID 
cleanrr$id <- (seq.int(nrow(cleanrr)))
#arousal data
rr.long.arousal <-  gather(data = cleanrr, key = condition, value = arousal, sad.arousal, happy.arousal, fear.arousal, tender.arousal, angry.arousal, factor_key=TRUE)
rr.long.arousal <- rr.long.arousal %>% select(contains("ID"),
                                        contains("alexithymia"),
                                        contains("ddf"),
                                        contains("dif"),
                                        contains("eot"),
                                        contains("condition"),
                                        contains("arousal"),
                                        contains("depression"),
                                         contains("ddf"),
                                        contains("dif"),
                                        contains("eot"))
xfun::pkg_attach2("plyr")
rr.long.arousal$condition <- mapvalues (rr.long.arousal$condition, from = c ("sad.arousal", "happy.arousal", "fear.arousal", "tender.arousal", "angry.arousal"), to = c("Sad", "Happy", "Fearful", "Tender", "Angry"))

rr.long.arousal$condition<-relevel(rr.long.arousal$condition, "Tender")
levels(rr.long.arousal$condition)
```
## No depression in model
```{r arousal glmm}
xfun::pkg_attach2("lme4")
arousalinteract <- glmer(arousal ~ 1 + alexithymia + condition + alexithymia*condition + (1|id), data = rr.long.arousal)
tab_model(arousalinteract)
xfun::pkg_attach2("lmerTest")
a.test <- as(arousalinteract,"merModLmerTest")
anova(a.test)

xfun::pkg_attach2("interactions")
interactions::sim_slopes(model = arousalinteract, pred = alexithymia , modx = condition, confint = TRUE)
```
## Plot model
```{r plot arousal}
xfun::pkg_attach2("jtools")
arousalplot <- interactions::interact_plot(model = arousalinteract, pred = alexithymia, modx = condition, interval = TRUE) + 
  theme_apa() + 
  geom_hline(yintercept = 0, linetype = "dotted") + labs (x = "Alexithymia", y = "Rated Arousal") 
arousalplot
```

##Depression in model
```{r arousal with depression}
arousalinteractdep <- glmer(arousal ~ 1 + depression + alexithymia + condition + alexithymia*condition + (1|id), data = rr.long.arousal)
anova(arousalinteract, arousalinteractdep) %>% as.data.frame() %>% sjPlot::tab_df()
```

#Valence GLMM
## Valence data reshape
```{r valence reshape}
rr.long.valence <- gather(data = cleanrr, key = condition, value = valence, sad.valence, happy.valence, fear.valence, tender.valence, angry.valence, factor_key=TRUE)
rr.long.valence <- rr.long.valence %>% select(contains("ID"),
                                        contains("alexithymia"),
                                        contains("condition"),
                                        contains("depression"),
                                        contains("valence"),
                                        contains("ddf"),
                                        contains("dif"),
                                        contains("eot"))
rr.long.valence$condition <- mapvalues (rr.long.valence$condition, from = c ("sad.valence", "happy.valence", "fear.valence", "tender.valence", "angry.valence"), to = c("Sad", "Happy", "Fearful", "Tender", "Angry"))

rr.long.valence$condition<-relevel(rr.long.valence$condition, "Tender")

levels(rr.long.valence$condition)
```
## Model fit
```{r valence glmm}
valenceinteract <- glmer(valence ~ 1 + alexithymia + condition + condition*alexithymia + (1|id), data = rr.long.valence)

reghelper::simple_slopes(valenceinteract)

sjPlot::plot_model(valenceinteract, type = "int", mdrt.values = "meansd", title = "Model Does Not Include Depression")

sjPlot::tab_model(valenceinteract, arousalinteract)

xfun::pkg_attach2("lmerTest")
v.test <- as(valenceinteract,"merModLmerTest")
anova(v.test) 


xfun::pkg_attach2("interactions")
interactions::sim_slopes(model = valenceinteract, pred = alexithymia , modx = condition, confint = TRUE)
```
##Plot Model
```{r valence plot}
valenceplot <- interactions::interact_plot(model = valenceinteract, pred = alexithymia, modx = condition, interval = TRUE) + 
  theme_apa() + 
  geom_hline(yintercept = 0, linetype = "dotted") + labs (x = "Alexithymia", y = "Rated valence") 
valenceplot
```

##Depression in model 
```{r valence with depression}
valenceinteractdep <- lmer(valence ~ 1 + depression + alexithymia + condition + alexithymia*condition + (1|id), data = rr.long.valence)
xfun::pkg_attach2("htmlTable")
write_tableHTML(tableHTML(mtcars), file = 'myfile.html')

anova(valenceinteract, valenceinteractdep) %>% as.data.frame() %>% sjPlot::tab_df()
```

## Print ggplot to word 

```{r}
xfun::pkg_attach2("rvg", "officer")
valencedoc <- read_pptx()
valencedoc <- add_slide(valencedoc, layout = "Title and Content", master = "Office Theme")
valencedoc <- ph_with_vg(valencedoc, ggobj = valenceplot,
                  type = "body")
print(valencedoc, target = "valenceplot.pptx")


arousaldoc <- read_pptx()
arousaldoc <- add_slide(arousaldoc, layout = "Title and Content", master = "Office Theme")
arousaldoc <- ph_with_vg(arousaldoc, ggobj = arousalplot,
                  type = "body")
print(arousaldoc, target = "arousalplot.pptx")
```




