---
title             : "Negative Valence Specific Deficits for the Perception of Musical Affect In Alexithymia"
shorttitle        : "Alexithymia and Musical Affect "

author: 
  - name          : "Joel L Larwood"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "School of Psychology, The University of Queensland, St Lucia, QLD, Australia, 4072"
    email         : "joel.larwood@uq.net.au"
  - name          : "Eric J Vanman"
    affiliation   : "1"
  - name          : "Genevieve A Dingle"

affiliation:
  - id            : "1"
    institution   : "School of Psychology, The University of Queensland"


authornote: |
  The pre-registration of this study can be viewed at https://osf.io/3myru/wiki/home/ a link to data and analysis script can be found at https://osf.io/zwsdj/  
  JL designed the study, conducted analyses and wrote the manuscript, EV and GD contributed to study design and the drfting of the manuscript. 
  
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["Negative Valence Specific Deficit in Alexithymia.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

  Alexithymia is a sub-clinical personality trait primarily characterized by a lack of words for emotional experiences. It is considered to consist of three facets: difficulties identifying feelings, difficulty describing feelings, and an externally oriented thinking style. The difficulty identifying and describing emotions facets can be seen to reflect cognitive deficits in the processing [@Goerlich-Dobre2015]. Alexithymia is related to reduced subjective awareness of bodily feelings but not the objective ability to monitor bodily sensations or changes [@Zamariola2018]. High levels of alexithymia have been further related to a reduced capacity for forming mental representations of emotions [@Ihme2014]. More broadly, alexithymia has been found to relate to the reduced ability to accurately label emotions [@Grynberg2012a]. These difficulties observed in alexithymia are particularly relevant within constructivist theories of emotion. 
  
  Constructivist theories of emotion, notably those of Barrett [-@Barrett2006; -@Barrett2017] informed by @Russell2003, posit that emotions are constructed in relation to bodily sensations, situational context and knowledge about what constitutes a specific emotion, such as sadness or anger. This ability to label an emotion is possible through emotion words which store conceptual information reducing uncertainty around an experience [@Barrett2007]. Vital, but not sufficient for the emotion construction process is the awareness of core affect [@Barrett2017; @Russell2003]. Core affect consists of two dimensions: valence, how pleasant or unpleasant a feeling or object is, and arousal, how energizing or activating a feeling or object is. @Russell2003 holds that all objects and events have an affective quality, and therefore can be considered along the dimensions of valence and arousal. However, not all object or events will allow for a change in core affect, perception or experience of an emotion. For instance, a landscape will be seen, or perceived, and be attributed an affective quality but this perception of will not necessarily lead to an emotion. For an emotion to either be experienced or perceived the affective quality must be categorized into an emotion. This categorization process involves considering previous instances of an emotion and evaluating against the current situation [@Barrett2006]. Emotion perception then has two factors, core affect and it’s integration with conceptual emotion knowledge.  
  
  Alexithymia, within Barrett’s (2006) conceptualization is then the inability to conceptualize core affect into an emotion category. Given that emotion concepts are informed by past experiences (situated conceptualisation) the conceptual deficits seen in alexithymia may, in part, stem from an earlier deficit in affect perception and a lack of integration of affective information with semantic representations of emotion concepts. A meta-analysis of neural activation during emotional stimuli presentation has revealed that higher scores on alexithymia are related to increased activation in the anterior cingulate gyrus. Furthermore decreased activation in the amygdala and dorsolateral prefrontal cortex was found during negative stimuli presentation as well as decreased activation of anterior insula during positive stimuli presentation. Lower grey-matter volume has also been found in the left middle temporal gyrus [@Grabe2014] but this has not been found to correspond to reduced activation during stimulus presentation [@vandervelde2013]. Through a constructionist lens these areas are involved in the cognitive production of emotion through the integration of interoceptive (internal) and extroceptive (external) sensations allowing for the realisation of core affect (ACC), attending to salient external cues (amygdala), concept knowledge (dMPFC), and interoceptive awareness (anterior insula)[-@Lindquist2012]. Therefore, it is not just the linguistic or conceptual networks of the brain that are compromised in alexithymia but also, importantly, areas that correspond to attending to and realising core affect.
  
  SELF REPORT STUDIES 
  ERP in there 
  
  MUSIC STUDIES 
    Bring in appraisal theory (Scherer 2005 - music always appraised as emotionally salient and therefore likely to have strong situated conceptualisation) 
    
   Music reveals itself as a ideal stimulus type to investigate the impact of alexithymia on early stages of the construction of emotion, as it is processed with an emotionally salient affective quality. Informed by constructionist emotion theory which posits that emotions are constructed through an integration of affective information, past experiences and conceptual knowledge the present study sought to reveal whether the existing findings of defects in emotion categorisation are also present on an affective level. SOMETHING ABOUT EMOTION CONCEPTS. Presenting participants with musical excerpts from five emotion categories varying on affective quality we hypothesised that alexithymia would disrupt affect processing, predicting that perceptions of valence and arousal would be more neutral as alexithymia increased regardless of the emotional category the musical stimuli represented. 
  
  
  
  
  to increased cognitive demand (higher anterior cingulate gyrus activation), decreased attention to negative stimuli (reduced amygdala activation), and reduced activation of interoceptive networks during positive stimuli presentation [@vandervelde2013]. 
  
  
  
  
  Keeping within constructionist theory, these results suggest that the on-line processing of emotions 

```{r setup, include = FALSE}
library("papaja")
library("tinytex")
```

```{r analysis-preferences}
# Seed for random number generation


set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r}
devtools::install_github("centerforopenscience/osfr", force = FALSE)
library(tidyverse)
osfr::osf_retrieve_file("nc9jp") %>% osfr::osf_download(overwrite = T)
dat <- read_csv("Data with Depression.csv")
```

```{r}
#count p's
nrow(dat)
#visualise missing data 
xfun::pkg_attach2("naniar")
dat %>% select(contains("MUVA"),
                   contains("MUAR"),
                   contains("TAS"),
                   contains("DASS")) %>% vis_miss()
#no missing data 
```


# Methods

```{r}
nopart <- nrow(dat)
meanage <- mean(dat$Age)
sdage <- sd(dat$Age)
nofemale <- dat %>% filter(Gender == 1) %>% nrow()
```

## Participants 
  Participants were `r nopart` living in the United Kingdom were sampled from Prolific (http://prolifc.ac). Participants had a mean age of `r meanage` ($SD `r sdage`) and `r nofemale` were female.  To be eligible for the study participants had to be ages 18 to 25 and residents of the United Kingdom, no exclusion criteria was applied. Participants were payed \pounds\ 1.25 for their participation in the online survey (15 minutes at \pounds\ 5 an hour) and the study was advertised as ‘exploring music and emotions’.

## Material

## Procedure

## Data analysis 
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References
```{r create_r-references}
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
