---
title: "Supplementary Materials"
author: "Joel Larwood"
date: "10/06/2019"
output:
  github_document: 
    toc: true
---

```{r setup}
library(TOSTER)
```


Here we present the Two One Sided Tests for the non-significant correlations reported between alexithymia and recall emotion lexicon. The interested reader may refer to Lakens, Scheel, and Isager (2018) for the details of this method. 

```{r}
TOSTER::powerTOSTr(alpha = .05, statistical_power = .8, N = 162) 

low <- -.2280002
high <- 0.2280002
```

#### Relationship between total alexithymia scores and total emotion words listed
```{r total tost}
#total emotions
TOSTER::TOSTr(n = 162, r = -.05, low_eqbound_r = low, high_eqbound_r = high) 
```

#### Relationship between total alexithymia scores and total positive emotion words listed
```{r positive tost}
#positive emotions  
TOSTER::TOSTr(n = 162, r = -.13, low_eqbound_r = low, high_eqbound_r = high) 
```


#### Relationship between total alexithymia scores and total negative emotion words listed
```{r negative tost}
#negative emotions
TOSTER::TOSTr(n = 162, r = .02, low_eqbound_r = low, high_eqbound_r = high)  
```

#### Relationship between Externally Oriented Thinking (EOT) and total emotion words listed 
```{r}
TOSTER::TOSTr(n = 162, r = .04, low_eqbound_r = low, high_eqbound_r = high)  
```

#### Relationship between Externally Oriented Thinking (EOT) and total positive emotion words listed 
```{r}
TOSTER::TOSTr(n = 162, r = .03, low_eqbound_r = low, high_eqbound_r = high)  
```

#### Relationship between Externally Oriented Thinking (EOT) and total negative emotion words listed 
```{r}
TOSTER::TOSTr(n = 162, r = .03, low_eqbound_r = low, high_eqbound_r = high)  
```

#### Relationship between Difficulty Describing Feelings (DDF) and total emotion words listed 
```{r}
TOSTER::TOSTr(n = 162, r = -.06, low_eqbound_r = low, high_eqbound_r = high)  
```

#### Relationship between Difficulty Describing Feelings (DDF) and total negative emotion words listed
```{r}
TOSTER::TOSTr(n = 162, r = .05, low_eqbound_r = low, high_eqbound_r = high)  
```

#### Relationship between Difficulty Identifying Feelings (DDF) and total emotion words listed 
```{r}
TOSTER::TOSTr(n = 162, r = -.08, low_eqbound_r = low, high_eqbound_r = high)  
```

#### Relationship between Difficulty Identifying Feelings (DDF) and total positive emotion words listed 
```{r}
TOSTER::TOSTr(n = 162, r = -.13, low_eqbound_r = low, high_eqbound_r = high)  
```

#### Relationship between Difficulty Identifying Feelings (DDF) and total negative emotion words listed 
```{r}
TOSTER::TOSTr(n = 162, r = -.02, low_eqbound_r = low, high_eqbound_r = high)  
```